---
title: "Our model repository"
output: 
  html_document:
    code_folding: show
    theme:
      bg: "#f8f8f8"
      fg: "#282828"
      primary: "#282828"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)

if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
```

## Model repository

We have three models in production right now. You can look at their individual model cards to understand:

- Model details
- Intended use and how to use it
- Important aspects/factors
- Performance metrics
- Training data & evaluation data
- Quantitative analyses
- Ethical considerations
- Caveats & recommendations

## Model repository {.tabset .tabset-pills}

Our models

### Store revenue prediction

Brief description of model

```{r}
library(tidyverse)
library(gt)
tibble(
    model_name = "Store predictions",
    version = "20230220T121352Z-9f8f2",
    last_updated = "2023-02-20",
    about_model = c("https://www.bbc.com/news")
) |> 
    mutate(
        about_model = map(about_model, ~ htmltools::a(href = .x, "Model card")),
        about_model = map(about_model, ~ gt::html(as.character(.x)))) |> 
    gt::gt() |> 
    cols_label(
        model_name = "Model name",
        version = "Version",
        last_updated = "Last updated",
        about_model = "About model"
    )
```

### Sales forecasting model

Brief description of model

```{r}
tibble(
    model_name = "Sales forecasting model",
    version = "20230220T121352Z-9f8f2",
    last_updated = "2023-02-20",
    about_model = c("https://www.bbc.com/news")
) |> 
    mutate(
        about_model = map(about_model, ~ htmltools::a(href = .x, "Model card")),
        about_model = map(about_model, ~ gt::html(as.character(.x)))) |> 
    gt::gt() |> 
    cols_label(
        model_name = "Model name",
        version = "Version",
        last_updated = "Last updated",
        about_model = "About model"
    )
```

### Store clustering model

Brief description of model

```{r}
tibble(
    model_name = "Clustering model",
    version = "20230220T121352Z-9f8f2",
    last_updated = "2023-02-20",
    about_model = c("https://www.bbc.com/news")
) |> 
    mutate(
        about_model = map(about_model, ~ htmltools::a(href = .x, "Model card")),
        about_model = map(about_model, ~ gt::html(as.character(.x)))) |> 
    gt::gt() |> 
    cols_label(
        model_name = "Model name",
        version = "Version",
        last_updated = "Last updated",
        about_model = "About model"
    )
```
